---
name: Berrit
surname: Kievith
position: "Student"
pronouns: she/her
address: "21 jumpstreet"
phone: +1 22 3333 4444
www: 
email: "berrit.kievit@gmail.nl"
twitter: 
github: berrit-github
linkedin: berrit kievith
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# introduction

Recently graduated student from the hogeschool Utrecht in Utrecht, Netherlands. Experience with PCR- , recombination Technics and cell culture upkeep. Additionally a minor in data science. looking for a job in genomic and or tumor science. Preferably one that offer growing opportunities and a balance between lab work an data science.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  " major in biomedical research and a minor in data science ", "2020-24", "Bachelor in life science", "Hogeschool Utrecht ,Utrecht, Netherlands",
   " specialized in clinical medical analytics and pathologie ", "2016-20", "intermediate vocational education: biomedical analyst", "ROC midden Nederland , Utrecht, Netherlands",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# work experience

```{r}
tribble(
  ~ bedrijf, ~ Year, ~ taak, ~ Where,
  " GEN DX", "2020 May-Jul", "Production technician ", "Utrecht, Netherlands",
  " GEN DX", "2019 sep - 20May", "internship production technician", "Utrecht, Netherlands",
  " OLVG hospital", "2019 Feb - 19Jun", "internship analyst patholigie department", "Amsterdam, Netherlands",
) %>%
  detailed_entries(bedrijf, Year, taak, Where)
```

# Miscellaneous

## languages
* Dutch, mother tongue
* English, B1 level

## other skills
* First aid licence (oct 2024)
* certified life guard

## Hobby's
* I enjoy cozy gaming and knitting in my free time. 
* For a more active life style I enjoy to swim. 






